Fast Radio Burst Cosmology

### 2014-07-24 writeup/dm_angular_ps.tex
New paper structure outline including Ue-Li's 3d seconds order statistics.

@@

>>>>

\section{Preliminaries}

@@

\section{2D statistics}
% Need beter section title.

Here we consider two dimentional statistics where the cosmological information
lies in the correlations between dispersion measures at a given angular
separation.  The information that is in principle available in the angular
clustering of the FRB events is ignored.

As a cosmological probe this almost perfectly analogouse to the weak lensing 
of galaxies.
We wish to estimate the line of site electron column density,
which, like lensing shear, is an integral along the line-of-site to a source at an
uncertain redshift. Our observerable the dispersion measure, like galaxy
elipticity, gives a noisy estimate.  In both cases the angular clustering of
the sources is ignored.

The dispersion measures of two different FRBs are correlated by two effects.
The first is correlations in the intervening line-of-site large-scale
structure.  This correlates the $D^{\delta_e}$ part of the dispersion measures.
The second effect is that two FRBs with small angular separation are likely to
be at small redshift separations if FRB events trace large-scale structure.
This correlates the $D^{\bar{n}_e}$ of the two FRBs.  In principle all
permutations of $D^{\bar{n}_e}$, $D^{\delta_e}$ and $D^{\rm src}$ should be
correlated to some degree, however we believe that the two effect described
here are the dominatnt contributions and defer investications of other effect
to future work.

\subsection{The dispersion measure angular power-spectrum}

\subsection{estimating the dispersion measure angular power-spectrum}

\subsection{sensitivity estimates}

\section{3D statistics}

3D clustering of FRBs using DM as distance proxy.

Dispersion measure space distortions.

\subsection{First order DM space distortions}

LOS election perturbations cause clusturing in unclustered FRBs.

\subsection{Second order DM space distortions}

LOS election perturbations cause non-stationarity/non-gaussianity in clustered FRBs.
